### 2025-01-13 reviewer-response.md

*Put the keys outside of the figures, not over the data lines.*

The figures have all been updated.

*Many horizontal and vertical lines in Table~2 should be removed to help with
readability.*

The table has been broken up and former sub-tables have been enlarged.

@@

*While there is implicitly a tree that is the key data structure, the tree
itself is never named or given a notation; the same is true of the root of
the tree.  The authors should review the requirements for defining proper
terminology and notation for a data structure and apply it consistently to
their data structure.*

we fixed this in pancakes, just backport it

*The authors appear to use the terms similarity and distance
interchangeably, though they are certainly different.  In particular, a
similarity is a measure (nominally, non-negative) that is (ideally) larger
the closer two data points are and, in some biological contexts, has no
upper bound.  Moreover, the use of a distance measure alone is inadequate
for the described algorithms.  On line 155, there is mention of the
geometric median of the points, but there may be no such median depending
on the space (set) containing the points of the data set.  For example,
there is no obvious median for a set of biological sequences.  The authors
must identify the actual spaces from which data sets can be extracted for
CAKES to work.*

We have added a definition of the geometric median in the paper, and have clarified how we interpret it for any metric space.
We have also fixed the language around similarity and distance, and have made sure to use the correct term in each context.

@@

*On line 141, there is a function defined for the local fractal dimension
(LFD), but it is not expressed in functional notation.  In other words, it
should start with $LFD(X,r_1,r_2)$, since it is clearly a function of all
three.  This functional notation should propagate throughout the rest of
the manuscript.  Much the same is true on line 142, where it should read
$B(X,q,r)$, not $B_X(q,r)$.  If makes little sense to put $X$ as a
subscript in this context.*

We have dropped the X since we are only dealing with one dataset.

@@

*In the algorithms, starting with Algorithm 2.1, the pseudocode style is
ugly.  Much better would be the pseudocode style from the fourth edition
of Introduction to Algorithms, CLRS.  Also, the description of $criteria$
is as a "stopping criteria", while the logic of the code has it as a
continuing criteria.  Please fix the pseudocode throughout.*

We evaluated the CLRS package, but did not see any aesthetic differences.
We have, however, increased the font size for the algorithm environments, so that it should be more legible.
We have also fixed the name for the criteria.

*Section 2.2 is meant to be the definition of the search problem(s), but
that is really only contained in the paragraph from lines 218 to 223. In
any case, it is essential to put the problem(s) to be solved earlier, that
is, first, before any description of the solutions with ideas such as
clusters.  This movement of text will require a bit of text refactoring at
a minimum.  Also, the sentence at lines 221 to 223 should be expanded in
full detail into a separate paragraph.  Finally, one assumes that the
integer $k$ or the number $\rho$ is a parameter to the corresponding
problem and should be mentioned as such.*

We have refactored the methods section to have a better flow, and have defined several terms in their proper place.
We have also removed $\rho$-NN search from the main body of the paper in order to focus exclusively on $k$-NN search.
The supplement now contains a section on the improvements to $\rho$-NN search.

@@

*There are no theorems in the manuscript, yet there are arguments for
quantities like the quality of the results or the time complexity that are
given without much precision.  It is better to give precise theorems or
propositions for each thing to be proved, with appropriate assumptions,
and to give precise proofs of same.*

state theorem, which is the time complexity, and formalize the argument into a proof

*The manuscript makes too much use of unfamiliar terminology taken from
earlier papers without defining terms.  For example, see line 233 and
Reference [18].  See also the paragraph at lines 306 to 310. All terms
used must be precisely defined in the manuscript to allow proper
assessment of the manuscript.*

We have addressed this by making the paper more self-contained.

@@

*The use of $\forall$, $\exists$, $\Leftrightarrow$, and other similar
logical operators is not appropriate in a manuscript that is not about
logic.  Spell out the meaning in English, and be creative.*

We respectfully disagree. These operators are also standard in set theory and functional analysis, and it is in this context that we use them. They are also standard in the algorithms literature, including CLRS. Unless this is editorial policy, we would prefer to keep them. We believe they lend precision.

*Near line 154, it is important to give an overview of your solution
strategy and, in particular, why clustering is used first.  Clustering is
a heavily overloaded word.  I would have chosen a more neutral term
instead of "cluster".*

We clearly define our clustering approach, and moreover, we build on prior work (some ours, some others) that relies on clustering. We respectfully would prefer to stay with the language we have here.

@@

*On line 178, there is the phrase "find the point ... in the sample".  Can
you make the entire paragraph more precise by giving notation for the
sample?*

We now refer to the sample as $S$.

*Section 2.1.1 overall is lacking in mathematical rigor.*

We have updated some language in this section.
This, combined with Algorithm 2.1, should provide a reasonable level of rigor.

@@

*In Section 2.1.3, the cost of assessing "criteria' is not counted in the
time complexity, but it must be.*

We have added a discussion of this in the corresponding complexity analysis.

@@

*In line 252, there is again mention of "real points" without any
indication of the meaning of "real".*

We have fixed language around "real points" and have clarified that the points are actual data points.

### 2025-01-13 sections/2-methods.tex
some stylistic changes because I'm being anal about the layout

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.65]{images/geometry/deltas.pdf}
    \caption{
        {\color{blue}$\delta$}, {\color{red}$\delta^{+}$}, and {\color{green}$\delta^{-}$} for a cluster $C$ and a query $q$.
        ${\color{blue}\delta} = f(q, c)$ is the distance from the query to the cluster center $c$.
        ${\color{red}\delta^{+}} = \delta + r$ is the distance from the query to the theoretically farthest point in $C$.
        ${\color{green}\delta^{-}} = \text{max}(0, \delta - r)$ is the distance from the query to the theoretically closest point in $C$.
    }
    \label{fig:methods:deltas}
\end{figure}

@@

In this section, we present three novel algorithms for exact $k$-NN search:
Repeated $\rho$-NN, Breadth-First Sieve, and Depth-First Sieve.
In these algorithms, we use $H$, for \textit{hits}, to refer to the data structure that stores the closest points to the query found so far, and $Q$ to refer to the data structure that stores the clusters and points that are still in contention for being one of the $k$ nearest neighbors.
The two Sieve algorithms also use some terminology defined and illustrated in Figure~\ref{fig:methods:deltas}.

@@

Now, so long as $\sum_{C \in Q} |C| < k$, we continue to perform tree-search, but instead of doubling $r$ on each iteration, we multiply it by a factor determined by the LFD in the vicinity of the query ball.
In particular, we increase the radius by a factor of
\begin{equation}
    \min \left(2, \left( {\frac{k}{\sum_{C \in Q} |C|}} \right)^{\mu^{-1}} \right)
    \label{eq:methods:repeated-rnn-factor}
\end{equation}
where $\mu$ is the harmonic mean of the LFD of the clusters in $Q$.
We use the harmonic mean to ensure that $\mu$ is not dominated by outlier clusters with very high LFD.
We cap the radial increase at 2 to ensure that we do not increase the radius too quickly in any single iteration.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated $\rho$-NN($\mathcal{R}$, $q$, $k$)} % give the algorithm a caption
    \label{alg:methods:repeated-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \Require $\mathcal{R}$, the root cluster
        \Require $q$, a query
        \Require $k$, the number of neighbors to find
        \State $r \Leftarrow radius$ of $\mathcal{R}$
        \State $r \Leftarrow$ $\frac{r}{|\mathcal{R}|}$
        \Loop
            \State $Q \Leftarrow$ tree-search($\mathcal{R}$, $q$, $r$)
            \If{$Q \neq \emptyset$}
                \State \textbf{break}
            \EndIf
            \State $r \Leftarrow 2 \cdot r$
        \EndLoop
        \Loop
            \If{$\sum_{C \in Q} |C| >= k$}
                \State \textbf{break}
            \EndIf
            \State $\mu \Leftarrow |Q| \cdot \left( \sum_{C \in Q} LFD(C)^{-1} \right)^{-1}$
            \State $r \Leftarrow r \cdot \min \left( 2, \left( {\frac{k}{\sum_{C \in Q} |C|}} \right)^{\mu^{-1}} \right)$
            \State $Q \Leftarrow$ tree-search($\mathcal{R}$, $q$, $r$)
        \EndLoop
        \State $H \Leftarrow \text{leaf-search}(Q, q, r)$
        \State \textbf{sort} $H$ by non-decreasing distance to $q$
        \State \textbf{return} The first $k$ points in $H$
    \end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.65]{images/geometry/deltas.pdf}
    \caption{
        {\color{blue}$\delta$}, {\color{red}$\delta^{+}$}, and {\color{green}$\delta^{-}$} for a cluster $C$ and a query $q$.
        ${\color{blue}\delta} = f(q, c)$ is the distance from the query to the cluster center $c$.
        ${\color{red}\delta^{+}} = \delta + r$ is the distance from the query to the theoretically farthest point in $C$.
        ${\color{green}\delta^{-}} = \text{max}(0, \delta - r)$ is the distance from the query to the theoretically closest point in $C$.
    }
    \label{fig:methods:deltas}
    \vskip -0.5in
\end{figure}

@@

In this section, we present three novel algorithms for exact $k$-NN search:
Repeated $\rho$-NN, Breadth-First Sieve, and Depth-First Sieve.
In these algorithms, we use $H$, for \textit{hits}, to refer to the data structure that stores the closest points to the query found so far, and $Q$ to refer to the data structure that stores the clusters and points that are still in contention for being one of the $k$ nearest neighbors.
These algorithms also use some terminology defined and illustrated in Figure~\ref{fig:methods:deltas}.

@@

Now, so long as $\sum_{C \in Q} |C| < k$, we continue to perform tree-search, but instead of doubling $r$ on each iteration, we multiply it by a factor determined by the LFD in the vicinity of the query ball.
In particular, we increase the radius by a factor of
\begin{equation}
    \min \left(2, \left( {\frac{k}{\sum_{C \in Q} |C|}} \right)^{\mu} \right)
    \label{eq:methods:repeated-rnn-factor}
\end{equation}
where $\mu$ is the multiplicative inverse of the harmonic mean of the LFD of the clusters in $Q$, i.e.,\,$\mu = |Q| \cdot \sum_{C \in Q} \big( LFD(C)^{-1} \big)$.
We use the harmonic mean to ensure that $\mu$ is not dominated by outlier clusters with very high LFD.
We cap the radial increase at 2 to ensure that we do not increase the radius too quickly in any single iteration.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Repeated $\rho$-NN($\mathcal{R}$, $q$, $k$)} % give the algorithm a caption
    \label{alg:methods:repeated-rnn} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \Require $\mathcal{R}$, the root cluster
        \Require $q$, a query
        \Require $k$, the number of neighbors to find
        \State $H \Leftarrow [\ ]$, a max-heap of size $k$ to contain neighbors prioritized by distance to the query
        \State $r \Leftarrow radius$ of $\mathcal{R}$
        \State $r \Leftarrow$ $\frac{r}{|\mathcal{R}|}$
        \State $Q \Leftarrow$ tree-search($\mathcal{R}$, $q$, $r$)
        \While{$\sum_{C \in Q} |C| < k$}
            \If{$Q = \emptyset$}
                \State $r \Leftarrow 2 \cdot r$
            \ElsIf{$\sum_{C \in Q} |C| >= k$}
                \State $\mu \Leftarrow |Q| \cdot \sum_{C \in Q} \big( LFD(C)^{-1} \big)$
                \State $r \Leftarrow r \cdot \min \bigg( 2, \left( {\frac{k}{\sum_{C \in Q} |C|}} \right)^{\mu} \bigg)$
            \EndIf
            \State $Q \Leftarrow$ tree-search($\mathcal{R}$, $q$, $r$)
        \EndWhile
        \State $H \Leftarrow \text{leaf-search}(Q, q, r)$
        \State \textbf{return} $H$ as a list
    \end{algorithmic}
\end{algorithm}

@@

\vskip 0.1in

### 2025-01-13 sections/4-results.tex
some stylistic changes because I'm being anal about the layout

\begin{figure}
    \captionsetup[subfigure]{aboveskip=-15pt,belowskip=-3pt}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/fashion-mnist.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/glove-25.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/sift.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/random.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/silva-SSU-Ref.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/radio-ml.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \vskip 0.005in
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{images/lfd/legend.png}
        \label{fig:results:lfd-legend}
    \end{subfigure}%
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by percentiles of local fractal dimension and weighted by the cardinalities of the clusters.
    Note that the y-axis is different for the random dataset.}
    \label{fig:results:lfd-plots}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/fashion-mnist_PermutedBall_10_throughput.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/glove-25_PermutedBall_10_throughput.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/random_PermutedBall_10_throughput.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/silva-SSU-Ref_PermutedBall_10_throughput.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/radio-ml_Ball_10_throughput.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{plots/legend.png}
        \label{fig:results:scaling-legend}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    For HNSW and ANNOY, we were not able to take measurements for each cardinality because building the index required more RAM than was available (i.e.,\,more then 512GB).
    For linear search with CAKES, we only report the throughput for a few of the initial multipliers because the trend is clear.}
    \label{fig:results:scaling-plots}
\end{figure}

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_throughput.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:fashion-mnist-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_counts.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:glove-25-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_throughput.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:sift-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_counts.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:random-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_throughput.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:silva-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_counts.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:radioml-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{images/distance_counts/legend.png}
        \label{fig:results:counts-legend}
    \end{subfigure}%
    \caption{Number of distance computations across four clustering strategies and three search algorithms on the Fashion-Mnist dataset.
    Adding the instrumentation to count the number of distance computations had the side-effect of significantly slowing down the search algorithms compared to those reported in Figure~\ref{fig:results:scaling-plots}.
    The left column shows the throughput in queries per second, while the right column shows the mean number of distance computations per query.
    The x-axis represents increasing cardinality of the dataset.}
    \label{fig:results:distance-counts}
\end{figure}

>>>>

\begin{figure}
    \captionsetup[subfigure]{aboveskip=-15pt,belowskip=-3pt}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/fashion-mnist.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/glove-25.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/sift.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/random.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/silva-SSU-Ref.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/radio-ml.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \vskip -0.1in
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{images/lfd/legend.png}
        \label{fig:results:lfd-legend}
    \end{subfigure}%
    \vskip -0.1in
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by percentiles of local fractal dimension and weighted by the cardinalities of the clusters.
    Note that the y-axis is different for the random dataset.}
    \label{fig:results:lfd-plots}
    \vskip -0.4in
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/fashion-mnist_PermutedBall_10_throughput.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/glove-25_PermutedBall_10_throughput.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/random_PermutedBall_10_throughput.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/silva-SSU-Ref_PermutedBall_10_throughput.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{plots/radio-ml_Ball_10_throughput.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{plots/legend.png}
        \label{fig:results:scaling-legend}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    For HNSW and ANNOY, we were not able to take measurements for each cardinality because building the index required more RAM than was available (i.e.,\,more then 512GB).
    For linear search with CAKES, we only report the throughput for a few of the initial multipliers because the trend is clear.}
    \label{fig:results:scaling-plots}
\end{figure}

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_throughput.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:fashion-mnist-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_counts.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:glove-25-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_throughput.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:sift-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_counts.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:random-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_throughput.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:silva-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_counts.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:radioml-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{images/distance_counts/legend.png}
        \label{fig:results:counts-legend}
    \end{subfigure}%
    \caption{Number of distance computations across four clustering strategies and three search algorithms on the Fashion-Mnist dataset.
    Adding the instrumentation to count the number of distance computations had the side-effect of significantly slowing down the search algorithms compared to those reported in Figure~\ref{fig:results:scaling-plots}.
    The left column shows the throughput in queries per second, while the right column shows the mean number of distance computations per query.
    The x-axis represents increasing cardinality of the dataset.}
    \label{fig:results:distance-counts}
\end{figure}
